Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
Added points slide
added playoff image

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne Charrier, Michael Bowers, Clinton, Sam"
output: slidy_presentation 
---

@@

@@

>>>>

---
title: "Using Monte Carlo to estimate the effects of NHL rule changes"
author: "Kilbourne Charrier, Michael Bauers, Clinton, Sam"
output: slidy_presentation 
---

@@

# Point System
- Instead of basing ranking off of a team's win-loss record, the NHL tracks points for each team
- 2 points for win (regulation or overtime)
- 1 point for overtime loss
- 0 points for regulation loss

@@

![](Images/nhl-playoff-bracket.jpg)
